Privacy Analysis of a Mobile Sensor Application

### 2014-12-28 paper.tex
removed privacy type inferences (implicit privacy violations)

\TODO{MM:\\
- Shorten\\
- Remove Implicit Type Violations\\
- Update figure\\
- RG: Discuss alternative definitions of privacy\\
}

@@

\subsection{Privacy Type Inferences}

The above types of privacy types are not disjoint to each other.
For example if the location of a citizen is known it is possible to infer information about political associations (e.g. his visits to a party meeting).
In this section we explore possibilities how personal data can be inferred from each other.
Our findings are summarized in Figure \ref{figure:Implicit Privacy Violation Matrix}.

%\includegraphics{../diagrams/png/implicit-privacy-violation-matrix.png}
\input{./figures/Implicit-Privacy-Violation-Matrix}

\paragraph*{1. Privacy of The Person}

The Privacy of The Person is concerned with one's biometric privacy.
If this type is violated, following implicit violations are possible:

\begin{itemize}
\item [(1-5)]
  Privacy of Thoughts and Feelings. Some psychological diseases
  (e.g.~depression) have physiological impact. Such physiological
  patterns could be detected.
\end{itemize}

\paragraph*{2. Privacy of Behaviour and Action}

The Privacy of Behaviour and Action is concerned with one's social, political, religious, sexual, etc. activities.
If his type is violated, following implicit violations are possible:

\begin{itemize}
\item [(2-1)] Privacy of The Person.
  Religious practices which include body modifications (e.g.~circumcision).
\item [(2-5)] Privacy of Thoughts and Feelings.
  Social activities in general depend on a certain intellectual attitude.
  Such an activity is the expressions of such an attitude.
\item [(2-7)] Privacy of Association.
  Recording religious, political or sexual activities can reveal association with churches, political parties or sexual partners.
\end{itemize}

\paragraph*{3. Privacy of Communication}

The Privacy of Communication is concerned with not having such communication (correspondence or vis-a-vis) intercepted.
This is very broad type of privacy.
Depending on the contents of the intercepted communication every other type can be violated:

\begin{itemize}
\item [(3-1)] Privacy of The Person. Communication about body characteristics.
\item [(3-2)] Privacy of Behaviour and Action. Communication about social activities.
\item [(3-4)] Privacy of Data and Image.
  Communication containing one's passwords or other sensitive data.
\item [(3-5)] Privacy of Thoughts and Feelings.
  Communication of thoughts and feelings, e.g.~wiretapping a flirt or a catholic confession
  ritual.
\item [(3-6)] Privacy of Location and Space.
  Interception of face-to-face communication is only possible if one's location and space is violated (wiretapping).
\item [(3-7)] Privacy of Association.
  Communication about one's associations (family members, churches, etc.).
\end{itemize}

\paragraph*{4. Privacy of Data and Image}

The Privacy of Data and Image is concerned with one's data not being automatically available to others.
This also is a very broad type of privacy.
Depending of the data or image contents every other type can be violated:

\begin{itemize}

\item [(4-1)] Privacy of The Person.
  Images or stored biometric information reveal one's physical characteristics.
\item [(4-2)]Privacy of Behaviour and Action.
  Images or diaries can reveal one's social activities.
\item [(4-3)]Privacy of Communication.
  Modern communication systems usually contain some sort of archive function, e.g.~E-mail clients do not automatically delete messages.
  Such messages are data and reveal one's communication.
\item [(4-4)]Privacy of Thoughts and Feelings.
  Images can show one's emotional state.
\item [(4-5)]Privacy of Location and Space.
  Images can reveal one's location, e.g.~making a picture in front of the Eifel Tower.
\item [(4-6)]Privacy of Association. E-mail data can also reveal
  association.
\end{itemize}

\paragraph*{5. Privacy of Thoughts and Feelings}

The Privacy of Thoughts and Feelings is concerned with keeping such
thoughts and feelings secret. If this type is violated, following
implicit violations are possible:

\begin{itemize}
\item [(5-1)] Privacy of The Person.
  Thoughts and feelings can reveal medical conditions.
\item [(5-2)] Privacy of Behaviour and Action.
  Thoughts and feelings can reveal a certain attitudes which create a foundation for certain   social activities.
\item [(5-7)] Privacy of Association.
  Thoughts and feelings can reveal individual association, e.g amorous feelings for a certain person.
\end{itemize}

\paragraph*{6. Privacy of Location and Space}

The Privacy of Location and Space is concerned with one's right to move freely without being tracked and one's right to private places.
If this type is violated, following implicit violations are possible:

\begin{itemize}
\item [(6-1)] Privacy of The Person.
  Frequently visited doctors can reveal certain medical conditions, if such doctors are known specialsts.
  In general it could imply illness.
\item [(6-2)] Privacy of Behaviour and Action.
  Frequently visited places in general can reveal association and hence implies social activities.
\item [(6-3)] Privacy of Communication.
  If one's location is knwon, it is possible to intercept (wiretap) one's communication.
  This also may violate the right to private spaces.
\item [(6-4)] Privacy of Data and Image.
  If one's location is known, it is possible shoot pictures.
\item [(6-5)] Privacy of Thoughts and Feelings.
  Frequently visited persons may imply certain thoughts and feelings, e.g.~having a mistress.
\item [(6-6)] Privacy of Association.
  Frequently visited places can reveal associations simply by searching in maps or yellow-pages.
\end{itemize}

\paragraph*{7. Privacy of Association}

The Privacy of Association is concerned with one's right to associate with whomever one wants, without that association having recorded.
If this type is violated, following implicit violations are possible:

\begin{itemize}

\item [(7-1)] Privacy of The Person.
  Association with tattoo artists could imply having tattoos or other body modifications.
\item [(7-2)] Privacy of Behaviour and Action.
  Association with churches or political organizations could imply certain activities.
\item [(7-5)] Privacy of Thoughts and Feelings.
  Association with churches of political organizations could imply a certain intellectual attitude.
\end{itemize}

>>>>

\TODO{MM:\\
- Shorten\\
- DONE - Remove Implicit Type Violations\\
- Update figure\\
- RG: Discuss alternative definitions of privacy\\
}

@@
